Solving Consensus with OpenFlow

### 2015-03-06 inband-STN.tex
rewrite algs

\begin{algorithm}[t]
    \caption{Advanced Update Algorithm}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require update requests $U$
    \Ensure installed policy is consistent with previous one
    \If {first time}
		%\Do
		\Repeat
			\State $my\_cur\_id\gets$ unused entry id
    		\State $res \gets $ create entry with id $my\_cur\_id$
    	\Until{$res=False$}
    	%\doWhile{$res=False$}
    \EndIf
 		%\Do
 		\Repeat
 			\State $cur\_id\gets$ read current entry id
 			\State $cur\_policy\gets$ read current policy
 			\State $my\_next\_id\gets$ unused entry id
 			\State $new\_policy\gets$ apply update requests on $cur\_policy$
 			\startTransaction
	 			\State delete entry with id $1<<(\log n) + cur\_id$
	 			\State create entry with id $1<<(\log n) + my\_cur\_id$
	 			\State add $new\_policy$ rules conditioned on $metadata=my\_cur\_id$
	 			\State update policy selector to $my\_cur\_id$
 			\endTransaction
     		\State $res \gets $ commit transaction
     	\Until{$res=False$}
     	%\doWhile{$res=False$}
%   \vspace{3mm}

@@

>>>>

\begin{algorithm}[t]
    \caption{Advanced Update Algorithm}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require update requirements $U$, two entries containers CUR and NEXT.
    \Ensure installed policy is consistent with previous one
    \Repeat
			\State $my\_id\gets$ unused id (in both CUR and NEXT)
    		\State $res \gets $ NEXT.Add($my\_id$, True)
    \Until{$res=True$}
 		%\Do
 		\Repeat
 			\State $pid\gets$ read current policy id (only one in CUR)
 			\State NEXT.Add($pid$)
 			\If {$pid\notin CUR$}
 				\State {\bf continue} (restart loop)
 			\EndIf
 			\State $cur\_policy\gets$ read current policy
 			\State $new\_policy\gets apply\_update(cur\_policy,U)$
 			\startTransaction
	 			\State CUR.Delete($b_pid$)
	 			\State CUR.Add($my\_id$)
				\State NEXT.Delete($my\_id$, True)
	 			\State add $new\_policy$ rules %conditioned on $metadata=my\_a$
	 			%\State update policy selector to $my\_a$
 			\endTransaction
     		%\State $res \gets $ commit transaction
     	\Until{$res=True$}
     	%\doWhile{$res=False$}
%   \vspace{3mm}
			\Return

@@

\begin{algorithm}[t]
    \caption{Container Add abstraction}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require Container id $C$, entry id $i$, unique constrain (defaults to False) $b\_unique$, caller id $caller$.
%    \Ensure 
    		\State $value \gets C.i$
    		\State $mask \gets all-ones$
    		\State $cookie \gets C.i.caller$
    		\If {$b\_unique$}
    			\State $flag \gets 0$
    		\Else
    		    \State $flag \gets CHECK\_OVERLAP$
    		\EndIf
    					\State $cmd\gets FlowMod(match=(value,mask), operation = ADD, cookie, flag) $
			\Return cmd
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{Container Delete abstraction}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require Container id $C$, entry id $i$, unique constrain (defaults to False) $b\_unique$, caller id $caller$.
%    \Ensure 
    		\State $value \gets C.i$
    		\State $mask \gets all-ones$
    		\State $cookie \gets C.i.caller$
    		\If {$b\_unique$}
    			\State $cmd\gets FlowMod(match=(value,mask), operation=DELETE) $
    		\Else
    		    \State $cmd\gets FlowMod(match=(value,mask), operation=DELETE_STRICT, cookie) $
    		\EndIf

			\Return cmd
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{Advanced Update Algorithm2}
    \label{alg:template}
    \begin{algorithmic}[1]
    \Require update requirements $U$, two entries containers CUR and NEXT.
    \Ensure installed policy is consistent with previous one
    \If {first time}
		%\Do
		\Repeat
			\State $my\_id\gets$ unused id (in both CUR and NEXT)
    		\State $res \gets $ NEXT.Add($my\_id$, True)
    	\Until{$res=True$}
    	%\doWhile{$res=False$}
    \EndIf
 		%\Do
 		\Repeat
 			\State $pid\gets$ read current policy id (only one in CUR)
 			\State NEXT.Add($pid$)
 			\If {$pid\notin CUR$}
 				\State {\bf continue} (restart loop)
 			\EndIf
 			\State $cur\_policy\gets$ read current policy
 			\State $next\_id\gets$  unused id (in both CUR and NEXT)
 			\State $new\_policy\gets apply\_update(cur\_policy,U)$
 			\startTransaction
	 			\State CUR.Delete($b_pid$)
	 			\State CUR.Add($my\_id$)
				\State NEXT.Delete($my\_id$, True)
				\State NEXT.Add($next\_id$, True)
	 			\State add $new\_policy$ rules %conditioned on $metadata=my\_a$
	 			%\State update policy selector to $my\_a$
 			\endTransaction
     		%\State $res \gets $ commit transaction
     	\Until{$res=True$}
     	\State $my\_id\gets next\_id$
     	%\doWhile{$res=False$}
%   \vspace{3mm}

			\Return
    \end{algorithmic}
\end{algorithm}
